Machine Learning - Exercise 3

### 2021-02-21 exercise_3/presentation/presentation_ex3.tex
Updates from Overleaf

 \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/AM18HAS.JPG}
            \caption{A face from KDEF}
            \label{fig:KDEF_face}
        \end{subfigure}
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/FANHL.JPG}
            \caption{A face from AKDEF}
            \label{fig:AKDEF_face}
        \end{subfigure}
        \caption{}
        \label{fig:faces}
    \end{figure}
\end{frame}
\begin{frame}[fragile]{Evaluation}
\begin{itemize}
    \item Accuracy of Azure on labeled data roughly $0.76$
    \item attack set: starting with $2000$ up to $13961$
    \item Test set: $4654$
\end{itemize}
\end{frame}
\begin{frame}[fragile]{Evaluation}
           \begin{figure}[h!]
                    \centering      \includegraphics[scale=0.8]{exercise_3/paper/images/accuracy_copy_Azure.png}
                    \caption{Accuracy of the copied network}
                    \label{fig:Ac_Azure}
            \end{figure}

@@

\end{frame}
\end{document}

>>>>

 \begin{figure}[h!]
        \centering
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/AM18HAS.JPG}
            \caption{A face from KDEF}
            \label{fig:KDEF_face}
        \end{subfigure}
        \begin{subfigure}[c]{0.45\textwidth}
            \centering
            \includegraphics[width=0.9\textwidth]{exercise_3/paper/images/FANHL.JPG}
            \caption{A face from AKDEF}
            \label{fig:AKDEF_face}
        \end{subfigure}
        \caption{}
        \label{fig:faces}
    \end{figure}
\end{frame}
\begin{frame}[fragile]{Evaluation}
\begin{itemize}
    \item Accuracy of Azure on labeled data roughly $0.76$
    \item attack set: starting with $2000$ up to $13961$
    \item Test set: $4654$
    \item one hour including queries
\end{itemize}
\end{frame}
\begin{frame}[fragile]{Evaluation}
           \begin{figure}[h!]
                    \centering      \includegraphics[scale=0.8]{exercise_3/paper/images/accuracy_copy_Azure.png}
                    \caption{Accuracy of the copied network}
                    \label{fig:Ac_Azure}
            \end{figure}

@@

\end{frame}
\subsection[Cats and dogs]{Cats and dogs}
\begin{frame}[fragile]{Cats and dogs Model}
\begin{itemize}
\item CNN home trained on $25\,000$ images
\item Accuracy: $0,821$
\end{itemize}
\end{frame}
\begin{frame}[fragile]{Evaluation}
                \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.49\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat_domain.png}
                \caption{Accuracy using only problem domain}
                \label{fig:Accuracy_Cat_domain}
            \end{subfigure}
            \begin{subfigure}[c]{0.49\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Accuracy_copy_cat.png}
                \caption{Accuracy using mixed instances }
                \label{fig:Accuracy_cat_mix}
            \end{subfigure}
            \caption{Accuracy of Copycat Attack on second data set}
            \label{fig:accuracy_cat}
        \end{figure}
\end{frame}
\begin{frame}[fragile]{Evaluation}
       \begin{figure}[h!]
            \centering
            \begin{subfigure}[c]{0.49\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat_domain.png}
                \caption{Equality using only problem domain}
                \label{fig:Equality_cat_domain}
            \end{subfigure}
            \begin{subfigure}[c]{0.49\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{exercise_3/paper/images/Equality_copy_cat.png}
                \caption{Equality using mixed instances}
                \label{fig:Equality_cat_mix}
            \end{subfigure}
            \caption{Equality of Copycat Attack on second data set}
            \label{fig:equality_cat}
        \end{figure}
\end{frame}
\begin{frame}[fragile]{runtime}
    \begin{figure}[h!]
        \centering      \includegraphics[scale=0.4]{exercise_3/paper/images/Time_copy_cat.png}
        \caption{Time needed to extract a model}
        \label{fig:time_cat}
    \end{figure}
\end{frame}

\end{document}
